---
title: "Index"
author: "ZACHARY_ARENSON"
date: "11/11/2019"
output: html_document
---

```{r echo = FALSE, include = FALSE}
# Load results from the analysis
# errors and messages will not be printed given the `include = FALSE` option
source("analysis.R")
library("knitr")
```
# Report on U.S.Shootings

## Summary Info

*[Original Data Source](https://www.gunviolencearchive.org/reports/mass-shooting)
In 2018, `r shooting_num` shooting events were reported to have occured in the United States. From that number of shootings events, 'r total_lives_lost' people died during the shooting attacks. Meaning for every one attacker, a person died from the horrible consquences of society being unable to respond quick enough to a domestic attack. Out of the entire country, the state of 'r most_impacted_state' suffered the most injuries and deaths from a mass shooting event. More shootings occured depending on the state and, even cities such as 'r most_impacted_city' noted within the represented data. Concluding that certain areas struggle with mass shooting events on a larger level than other locations within the U.S. 

## Summary Table
```{r kable_example, echo = FALSE}
# "Return" the table to render it
kable(summary_table)
```

### Important Insights from Table
An important trend noticed regarding

## Description of a particular incident
Your report will include a paragraph (4+ sentences) of in-depth information about a particular (single) incident. You should provide your reader with relevant information from the dataset, such as the date and location of the incident, as well as the number of people impacted (injured, killed). You should include a link to at least one outside resource (not found in the data). Data in this paragraph should reference values that you calculate in R, and should not simply be typed as text into the paragraph.

## An interactive map
Before rendering your make, make sure to introduce the purpose of displaying the map in the report (e.g., what types of comparisons it affords).
`r interactive_map`
You'll build an interactive map that shows a marker at the location of each shooting. On your map, manipulate the size of the markers based on the underlying dataset (# injured, # killed, etc.). When hovered or clicked on, each point should provide at least 3 pieces of information about the incident (with a line break -- <br> -- between each piece of information) and no irrelevant information.

Below your map, you must note at least 2 insights revealed by the map.

Important: Choice of plotting library is up to you, though I suggest you consult the interactive visualization chapter of the book -- remember, the map must be interactive.  Please see chapter 17. 

## A plot of your choice
In addition to the interactive map, you will build an additional plot of your choice to answer a specific question about your data. You can do this using the package of your choice, such as ggplot2, plotly, bokeh, or others. The choices you make should be tied directly to the question you have about your data.  We recommend that you use ggplot2. 

Similarly to your map, you should integrate your plot seamlessly with the rest of your report, and reference/describe it in your text. Regardless of library, the chart should have meaningful and clear title, axis labels, and legend (if appropriate). 

You should provide a defense of why you chose the visual encodings of the chart (i.e., you chose a layout to answer a specific question), and list at least 2 insights gained from the chart.